\documentclass[10pt,stdletter,dateno]{newlfm}
\usepackage{kpfonts}
\usepackage{url}

\widowpenalty=1000
\clubpenalty=1000

\newlfmP{headermarginskip=20pt}
\newlfmP{sigsize=10pt}
\newlfmP{dateskipafter=20pt}
\newlfmP{addrfromphone}
\newlfmP{addrfromemail}
\PhrPhone{Phone}
\PhrEmail{Email}

\namefrom{Sajed Zarinpour Nashroudkoli}
\addrfrom{%
    \today\\[10pt]
    36 Poureslami Avenue\\
    Komeil Street\\
    Tehran 1353764371\\
    IRAN
}

\phonefrom{+98-935-218-82-08}
\emailfrom{sajed.zarinpour@gmail.com}

\addrto{%
Konrad-Adenauer-Straße 8\\
86836 Klosterlechfeld\\
GERMANY
}

\greetto{Dear Hiring Manager,}
\closeline{Sincerely,}
\begin{document}
\begin{newlfm}
    I am interested in the Backend Developer position at Barely Digital Operations GmbH. With a strong background in PHP development and experience in the Laravel framework, I can contribute effectively to your digital toll portals and traffic management solutions.

    I bring extensive experience in PHP, SQL, and database optimization, demonstrated through successful projects. 
    Throughout my career, I have maintained high coding standards and actively participated in code reviews, 
    ensuring optimal system performance and maintainability. For example, in my current role at Islamic Azad University Electronic Campus, I demonstrated my technical capabilities by significantly improving application performance, including reducing their ticketing system's response time from 3.6 seconds to 0.056 seconds. This achievement showcases my ability to optimize and scale systems effectively, a skill crucial for your service-oriented architecture. Furthermore, my role included developing 17 products, showcasing my ability to manage multiple projects and adapt to various requirements. My background in applied mathematics further enhances my problem-solving skills.
   
   I am particularly drawn to the role's focus on developing digital solutions for European transport systems and am excited about the opportunity to relocate to Augsburg. I value your commitment to supporting relocation and professional development.
   
   I am confident that my technical skills and enthusiasm for continuous learning would make me a valuable addition to your team. Thank you for considering my application; I look forward to your response.
   
   
   
%   Dear Hiring Manager,
%   
%   I am writing to express my interest in the Senior PHP Developer position at Centra. With a strong foundation in PHP development, a passion for building scalable, high-performance systems, and a commitment to writing clean, maintainable code, I am excited about the opportunity to contribute to your innovative API-based SaaS e-commerce platform.
%   
%   I bring extensive experience in PHP, SQL, and database optimization, demonstrated through successful projects. 
%   Throughout my career, I have maintained high coding standards and actively participated in code reviews, 
%   ensuring optimal system performance and maintainability. For example, in my current role at Islamic Azad University Electronic Campus, I demonstrated my technical capabilities by significantly improving application performance, including reducing their ticketing system's response time from 3.6 seconds to 0.056 seconds. This achievement showcases my ability to optimize and scale systems effectively, a skill crucial for your service-oriented architecture. Furthermore, my role included developing 17 products, showcasing my ability to manage multiple projects and adapt to various requirements. My background in applied mathematics further enhances my problem-solving skills.
%   
%   Centra’s ambition to build a world-class e-commerce platform resonates deeply with me. I am particularly drawn to your focus on modern PHP (8.3), high-performance optimization, and your plans to create a new GraphQL API. My experience with PHP, SQL, and database optimization aligns well with your tech stack, and I am eager to expand my skill set by contributing to your multi-tenant architecture and collaborating on cutting-edge projects. While I have not worked with Golang directly, I am enthusiastic about learning and applying new technologies to drive impactful results.
%   
%   What excites me most about Centra is your commitment to innovation and team collaboration. I value working in a non-hierarchical environment where ideas are shared openly, and I thrive in fast-paced, ambitious teams that prioritize efficient communication and high-quality output. The opportunity to work in your Wrocław office, connect face-to-face with talented colleagues, and be part of a company pushing boundaries in e-commerce is truly inspiring.
%   
%   I am confident that my technical expertise, problem-solving abilities, and passion for building exceptional software make me a strong fit for this role. I would welcome the opportunity to contribute to Centra’s mission and to grow alongside your talented team.
%   
%   Thank you for considering my application. I look forward to the opportunity to discuss how my skills and experiences align with your needs.
%   
%   Sincerely,
\end{newlfm}
\end{document}