\documentclass[10pt, a4paper]{article}

\usepackage{simplecv}


%\usepackage{showframe}
%\renewcommand\ShowFrameLinethickness{0.15pt}
%\renewcommand*\ShowFrameColor{\color{red}}



\usepackage {xcolor}
\begin{document}
	\name{ Sajed Zarinpour  Nashroudkoli}
	
	\contactInfo
	{Tehran, Tehran, Iran}
	{+98-935-218-8208}
	{sa.zarinpour@gmail.com}
	{https://www.linkedin.com/in/sajed-zarinpour}
	\section*{Summary}
	Experienced Laravel and PHP backend developer with a strong background in web application development and database management. Proven ability to design, develop, and optimize high-performance web applications and systems. Skilled in working with various APIs, databases, and technologies, including RESTful APIs, MySQL, and Elasticsearch. Experienced in code reviews and maintaining high-quality standards. Possesses a Master of Science in Applied Mathematics, demonstrating strong analytical and problem-solving skills. Fluent in English and eager to contribute to innovative traffic management and toll system solutions.
	
	\section*{Skills}
	\aside{PHP/Laravel}{\skills{Laravel, Symphony, PHP, RESTful APIs}}
	\aside{Database}{\skills{MySQL, MSSQL, Elasticsearch}}
	\aside{Web Development}{\skills{Backend Development, API Integration, Scaling Systems}}
	\aside{Other}{\skills{Git, Linux, Docker, Code Review, Agile Methodologies}}
% \section*{Summary}
% Highly motivated and experienced Laravel backend developer with a strong background in web development and database management. Proven ability to design, develop, and optimize high-performance web applications and systems.  Experienced in working with various APIs and technologies, including RESTful APIs, MySQL, and Elasticsearch.  Possesses a Master of Science in Applied Mathematics, demonstrating strong analytical and problem-solving skills.

% \section*{Skills}
% \aside{PHP/Laravel}{\skills{Laravel, Symphony, Moodle}} % Emphasize Laravel
% \aside{Database}{\skills{MSSQL, MySQL, Elasticsearch}}
% \aside{JavaScript}{\skills{ES2021, Node.js, jQuery}}
% \aside{Other}{\skills{Linux, Git, Postman, Stimulsoft, Docker, Draw.io}}

\section*{Experiences}
\expEntry
{Present\\Apr. 2024}
{System Designer/Web Developer}
{\href{https://int.ec.iau.ir/en/homepage/}{Islamic Azad University Electronic Campus}}
{Tehran}
{
    \explist{
        Upgraded and refactored \href{http://ticket.iauec.ac.ir/}{IAU ticketing system}, improving its PLT from 3.6 Sec to 0.056 Sec;
        Contributed to the development of 17 products, including \href{https://vadaroom.ec.iau.ir/v2/}{vadaroom.ec.iau.ir} and \href{https://vadana.ec.iau.ir}{vadana.ec.iau.ir};
        Analyzed products for security vulnerabilities and performance bottlenecks;
        % Developed Moodle plugins, such as academic course roadmaps and public session rooms;
        Designed a custom project management system with a specific focus on monitoring tasks of sub-divisions;
        Designed and implemented performance tests for BBB load balancer servers to deliver a robust experience in online classes for students.
    }
    \textcolor{gray}{\skills{Laravel, Symphony, Redis, Moodle, PHP, MySQL, Linux, Swagger, PHPDoc, Apache JMeter, Nginx, CI/CD, Docker}}
}

\expEntry
{March 2024\\Dec. 2023}
{Laravel Backend Developer} % Highlight Laravel again
{Motegharen}
{Guilan}
{
    \explist{
        Implemented an online Learning Management System by developing a Laravel package to interact with the Spotplayer API
        % Empowered \href{https://ayandeyesabz.com/}{ayandeyesabz.com} notifications with SMS using \href{https://www.melipayamak.com/}{Meli Payamak}.
    }
    \textcolor{gray}{\skills{Laravel, Git, REST API}}
}
	
	
	\expEntry
	{Nov. 2023\\Jan. 2022}
	{Compulsory Military Service}
	{Iranian Traffic Police}
	{Tehran}{}
	
	\expEntry
	{Nov. 2021\\Dec. 2020}
	{Database Analyst / Developer}
	{\href{https://www.linkedin.com/company/tavanasys/}{Tavana System}}
	{Zanjan}
	{
		\explist{ 
			Used elastic search for searching over routes and stops of school bus project;
			Design database schema for financial and warehousing section of an ERP for a private company;
			Impelemented main procedures for all data related actions such as overdue bill and warehouse handling;
			Crafted a custom markdown for special description system;
			Upgraded the reporting system using Stimulsoft to improve the quality of reports				
		}
		\textcolor{gray}{
			\skills{Python, Microsoft SQL server, Stimulsoft, Draw.io}
		}
	}
	
	
	\expEntry
	{Jan. 2020\\Nov. 2017}
	{Laravel Backend Developer}
	{ZarinSoft}
	{Rasht}
	{
		\explist{
			Design a Learning Management System using laravel and vue
			% Connected the shop to the banking system using Zarinpal api;
			% Broadcasted notifications using email and sms (using Kavenegar api);
			% Conducted regular website updates and maintenance to ensure functionality and usability
		}
		
		\textcolor{gray}{
			\skills{Laravel, Vuejs, MySQL, REST api}
		}
	}
	
	% \expEntry
	% {Nov. 2017\\Oct. 2015}
	% {Django Backend Developer}
	% {ZarinSoft}
	% {Rasht}
	% {
	% 	\explist{
	% 		Contributed to the developer community in Stackoverflow to reach the top 30\% users;
	% 		Fostered the growth of members' skills through periodic learning/Q\&A sessions
	% 	}
		
	% 	\textcolor{gray}{
	% 		\skills{Python, Django, MySQL, MongoDB}
	% 	}
	% }
	\expEntry
	{Nov. 2017\\Apr. 2010}
	{Early Career Development}
	{Various Companies}
	{Rasht / Bandar Anzali}
	{
		\explist{
			Innovated a \href{https://github.com/sajed-zarrinpour/Number-Partitioning/blob/master/Graph.md}{new definition of graphs} to solve the classical NP-hard problem of \href{https://github.com/sajed-zarrinpour/Number-Partitioning/tree/master}{number partitioning} implemented in C++;
			Developed the "Mahsa" integrated library system
			% Gained experience in Django and Python web development (ZarinSoft).;
			% Explored various technologies including C++, VB.NET, and SQL Server;
		}
		\textcolor{gray}{\skills{Python, Django, C++, VB.NET, SQL Server}}
	}

	% \expEntry
	% {Dec. 2015\\Apr. 2010}
	% {Freelancer}
	% {Freelancer}
	% {Bandar Anzali}
	% {
	% 	\explist{
	% 		Produced Mahsa integrated library system for a private library;
	% 		Innovated a \href{https://github.com/sajed-zarrinpour/Number-Partitioning/blob/master/Graph.md}{new definition of graphs} to solve the classical NP-hard problem of \href{https://github.com/sajed-zarrinpour/Number-Partitioning/tree/master}{number partitioning} implemented in C++
	% 	}
		
	% 	\textcolor{gray}{
	% 		\skills{Python, C++, Microsoft SQL Server, VB.NET}
	% 	}
	% }
	
	\section*{Published Packages}
\packageEntry
	{2024}
	{
		\href{https://packagist.org/packages/sajed-zarinpour/spotplayer}{sajed-zarinpour/spotplayer}, (A wrapper for spotplayer.ir video service (DRM) API).
	}
	{ 		
		\skills{PHP, Laravel} \\
	}
	\packageEntry
	{2024}
	{
		\href{https://packagist.org/packages/sajed-zarinpour/db}{sajed-zarinpour/db}, (A simple yet powerfull database adaptor).
	}
	{ 		
		\skills{PHP} \\
	}

	\section*{Education} 
	\eduEntry
	{Oct. 2020\\Sep. 2017}
	{M.Sc. in Applied Mathematics}
	{Institute for Advanced Studies in Basic Sciences, Iran}
	{Numerical Method for Solving PDEs with Uncertainty Using Neural-Network}
	{ 
		\explist{
			Impelemented a new layer for padding inputs using tf 
		}
		
		\skills{Python, Numpy, Bash, TensorFlow, Keras, Matplotlib, Octave, Latex} \\
	}
	
	\eduEntry
	{Sep. 2017\\Sep. 2012}
	{B.Sc. in Applied Mathematics}
	{University of Guilan, Iran}
	{Study on GMDH Algorithm for Stock Price}
	{ 
		\skills{MATLAB (Octave)}
	}
	
	%	\section*{Reaserch \& Interests}
	%	\interestslist
	%	{
		%		% research and interests
		%		Mathematical Modeling,
		%		Biological Systems \& Oncology,
		%		Finite Element Method, 
		%		Numerical Analysis,
		%		Deep Learning,
		%		Inverse Problems
		%	}
	
	
	%	\section*{Schools \& Conferences}
	
	%		\confEntry{2020}{ IASBS Student Presentations in English \\\normalfont \skills{On Solving Partial Differential Equations using Neural Networks} }{ Institute for Advanced Studies in Basic Sciences }	
	
	%		\centerline{***} %\slimseperator
	
	%		\confEntry{2021}{ An Introduction to Variational Analysis (Summer School) }{ Miami University, Urumia University of Technology }
	
	%		\confEntry{2020, 2021}{ One World IMAGINE seminars }{ Siam }
	
	%		\confEntry{2020}{ Solving inverse problems with deep learning }{ UC Berkeley Applied Math Seminar }
	
	%		\confEntry{2019}{ Introduction to Data Science in R }{ Institute for Advanced Studies in Basic Sciences }
	
	%		\confEntry{2019}{ From Biophysical Modeling to Simulation Codes (Winter School) }{ Graz university, Isfahan University of Technology }
	
	
	\section*{Languages}
	
	\languageEnry{ English }{ Upper Intermediate\\ }
	\selfAssessedEng{C1}{B2}{C1}{C1}{C1} % Listening, Reading, Spoken Interaction, Spoken Production, Writing

	%
	%	\section*{References}
	%		Available on Request
	%	\input{refrences}
	
\end{document}